{\LARGE Model Selection for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-02 Paper/main.tex
Rewriting motivation, small introduction on roughness penalties, literature reveiw

	\subsection{Inner Products and Hilbert Spaces}
	Let $\mathbb{V}$ be a vector space over some field of scalars $\mathbb{F}$. In the following we restrict our analysis to the case of $\mathbb{F} = \mathbb{R}$. A function $\langle \cdot, \cdot \rangle : \mathbb{V} \times  \mathbb{V} \rightarrow \mathbb{F}$ is called an inner product, if $\forall v, v_1, v_2 \in \mathbb{V}$ and $a_1, a_2 \in \mathbb{F}$ the following properties hold.

@@

	A vector space with an associated inner product is called an inner product space. {\color{red}[verbatim quote!]}
	The inner product naturally defines a norm and an associated distance on the vector space as follows.

@@

	\subsection{Hilbert Space of Square-Integrable Functions{\color{orange} $\mathbb{L}^2[0,1]$ space and Random Function}}
	In functional data analysis, one Hilbert space of particular importance is the space of square-integrable functions on $[0,1]$ denoted $\mathbb{L}^2[0,1]$. To define it, look first at the measure space given by $([0,1], \mathcal{B}, \mu)$ where $\mathcal{B}$ is the Borel $\sigma$-algebra on $[0,1]$ and $\mu$ is the Lebesgue-measure. Then $\mathbb{L}^2[0,1]$ is the collection of all measurable functions $f$ on $[0,1]$ that fulfill the following condition.

@@

	$\mathbb{L}^2[0,1]$ is the function space that is most often used for theoretical considerations in functional data analysis without loss of generality. We also focus on the interval [0,1] for the purpose of this paper.	A random function defined on $\mathbb{L}^2[0,1]$ can be represented as
	a function $X : \Omega \rightarrow \mathbb{L}^2[0,1]$ which is defined on a common probability space $(\Omega, \mathcal{A}, P)$ where $\Omega$ is a sample sapce with $\sigma$-algebra $\mathcal{A}$ and a probability space $P$. The realized $X(\omega)(t)$ for every $t \in [0,1]$ is called a sample curve for the process. The collection of such sample curves constitutes a functional data set.
	%Trivially, it is possible to extend this to other closed intervals on the reals line, but there are also more complex generalizations. For the purpose of this paper we will focus on the typical case and assume that random functions are random variables realizing in $\mathbb{L}^2$ for some closed interval of the real numbers.

	%\begin{equation}
	%\{f(t,\omega) : t \in [0, 1], \omega \in \Omega\}
	%\end{equation}

	\subsection{Bases of $\mathbb{L}^2$ {\color{orange}Basis Representation for Functions}} 
	{\color{red} Maybe change title due to monomial and bspline basis not fulfilling this property.}
	As previously described, a basis of a Hilbert space can be used to express elements of the space using the corresponding Fourier expansion. Two examples of bases that are often used in practice to express / approximate elements of $\mathbb{L}^2[0,1]$  are explained in the following.

@@

	\paragraph{Monomial Basis}
	{\color{red} No shift parameter in implementation in fda.} Every result of monomial basis expansion is the Taylor series of some function. 
	This is the basis that is needed to build polynomials, one of the best-known ways to expand a function. The polynomial of the form

@@

	In reality these calculations are often done using basis representations of both the functional principal components $\hat{\nu}^m$ and the observations $x_i(t)$ leading to the following representation. For the sake of clarity the following equation assumes that the bases used for the expansion of both the observations and the coefficient function are true bases of $\mathbb{L}^2[0,1]$ and can therefore be used to express the corresponding objects exactly.

	\begin{equation}\label{FPCA_basis_expansion}
		\begin{split}
			\hat{\xi}_{i}^m & = \int_{0}^{1} {\color{red}\left( x_i(s) - \hat{\mu}(s)\right)} {\color{blue}\hat{\nu}^m(s)} \mathrm{d}s
			= \int_{0}^{1} {\color{red}\left(\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)\right)} {\color{blue}\left(\sum_{k \in \mathcal{L}} b_{k}^m \psi_{k}(s)\right)} \mathrm{d}s \\
			& = \int_{0}^{1} {\color{red}\left(\sum_{j = 1}^{J} a_{i,j} \phi_j(s) + \delta_i^J(s)\right)} {\color{blue}\left(\sum_{k = 1}^{K} b_{k}^m \psi_{k}(s) + \delta_{\beta}^K(s)\right)} \mathrm{d}s \\
			& = \sum_{j = 1}^{J} \left[a_{i,j}\sum_{k = 1}^{K} b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right] +  \sum_{k = 1}^{K} b_{k}^m \int_{0}^{1} \delta_i^J(s) \psi_{k}(s) \mathrm{d}s + \sum_{j = 1}^{J} a_{i,j} \int_{0}^{1}\phi_j(s) \delta_{\beta}^K(s) \mathrm{d}s
		\end{split}
	\end{equation}

@@

	\begin{equation}\label{score_approx}
			\hat{\xi}_{i}^m = \sum_{j = 1}^{L} \left[a_{i,j}\sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right] +  \sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \delta_i^L(s) \psi_{k}(s) \mathrm{d}s + \sum_{j = 1}^{L} a_{i,j} \int_{0}^{1}\phi_j(s) \delta_{\beta}^L(s) \mathrm{d}s
	\end{equation}

	And we can define the following objects:

	\begin{equation}
		\begin{split}
			\tilde{\xi}^{m,L}_{i} & := \sum_{j = 1}^{J} \left[a_{i,j}\sum_{k = 1}^{K} b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right] \\
			\delta_{\xi, i}^L & := \hat{\xi}_{i}^m - \tilde{\xi}^{m,L}_{i} = \sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \delta_i^L(s) \psi_{k}(s) \mathrm{d}s + \sum_{j = 1}^{L} a_{i,j} \int_{0}^{1}\phi_j(s) \delta_{\beta}^L(s) \mathrm{d}s \\
			\tilde{\nu}^{m,L}(t) & := \sum_{k = 1}^{L} b_{k}^m \phi_{k}(t) \quad \quad \quad
			\delta_{\nu, m}^L(t) := \hat{\nu}^m(t) - \tilde{\nu}^{m,L}(t)
		\end{split}
	\end{equation}

@@

	\subsubsection{Estimation using Basis-Representation}
	The most common way to make this problem tractable is via a basis representation of $\beta(t)$. Therefore, let $\{b_i(t) \: \vert \: i \in \mathcal{I}\}$ be a basis of $\mathbb{L}^2[0,1]$ and represent $\beta(t)$ in terms of this basis.

	\begin{equation}
		\beta(t) = \sum_{j \in \mathcal{I}} b_j \phi_j(t)
	\end{equation}

@@

	\begin{equation}
		\begin{split}
			Y(\omega) & = \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j = 1}^{J} b_j \phi_j(s) + \delta_{\beta}^{J}(s)\right)} X(\omega)(s) \right]\mathrm{d}s + \epsilon(\omega) \\
			& = \alpha + \sum_{j = 1}^{J} b_j \int_{0}^{1} \phi_j(s) X(\omega)(s) \mathrm{d}s +  \int_{0}^{1} \delta_{\beta}^{J}(s) X(\omega)(s) \mathrm{d}s + \epsilon(\omega)
		\end{split}
	\end{equation}

@@

	\begin{equation}\label{basis_exp_transf}
		\begin{split}
			Y(\omega) & = \alpha + \int_{0}^{1} {\color{blue}\beta(s)} {\color{red}X(\omega)(s)}\mathrm{d}s + \epsilon(\omega)
			 = \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} b_j  \phi_j(s)\right)} {\color{red}\left(\sum_{k \in \mathcal{L}} a_k(\omega)  \psi_k(s)\right)} \right]\mathrm{d}s + \epsilon(\omega) \\
			& = \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j = 1}^{J} b_j  \phi_j(s) + \delta_{\beta}^{J}(s)\right)} {\color{red}\left(\sum_{k = 1}^K a_k(\omega)  \psi_k(s) + \delta_{X}^{K}(\omega)(s)\right)} \right]\mathrm{d}s + \epsilon(\omega)\\
			& = \alpha + \sum_{j = 1}^J b_j \left[\sum_{k = 1}^K a_k(\omega) \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s\right] + \sum_{j = 1}^{J} b_j  \int_{0}^{1} \phi_j(s) \delta_{X}^{K}(\omega)(s) \mathrm{d}s\\
			& \quad \quad + \sum_{k = 1}^{K} a_k(\omega)  \int_{0}^{1} \delta_{\beta}^{J}(s)\phi_j(s) \mathrm{d}s + \epsilon(\omega)
		\end{split}
	\end{equation}

@@

	\begin{equation}
			\tilde{Z}_j(\omega) = \sum_{k = 1}^{L} \left[a_k(\omega) \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \right] \quad j = 1, \dots, L
	\end{equation}

@@

	\begin{equation}\label{simplified_model_basis_equation}
		\begin{split}
			Y(\omega) &= \alpha + \sum_{j = 1}^{J} b_j \tilde{Z}_j(\omega) + \sum_{j = 1}^{J} b_j  \int_{0}^{1} \phi_j(s) \delta_{X}^{K}(\omega)(s) \mathrm{d}s + \sum_{k = 1}^{K} a_k  \int_{0}^{1} \delta_{\beta}^{J}(s)\phi_j(s) \mathrm{d}s + \epsilon(\omega) \\
			& \approx \alpha + \sum_{j = 1}^{J} b_j \tilde{Z}_j(\omega) + \epsilon(\omega)
		\end{split}
	\end{equation}

@@

	\begin{equation}
		\begin{split}
			Y(\omega) &= \alpha + \int_{0}^{1} {\color{red}X(\omega)(s)} \beta(s) \mathrm{d}s + \epsilon(\omega)
			= \alpha + \int_{0}^{1} {\color{red}\left(\mu(s) + \sum_{m = 1}^{\infty} \xi^m(\omega) \nu^m(s)\right)} \beta(s) \mathrm{d}s + \epsilon(\omega)\\
			&= {\color{teal}\alpha + \int_{0}^{1} \mu(s) \beta(s) \mathrm{d}s} + \sum_{m = 1}^{\infty} \xi^m(\omega) {\color{violet}\int_{0}^{1} \nu^m(s) \beta(s) \mathrm{d}s} + \epsilon(\omega)
			= {\color{teal}\bar{\alpha}} + \sum_{m = 1}^{\infty} \xi^m(\omega) {\color{violet}\beta^m} + \epsilon(\omega)
		\end{split}
	\end{equation}

@@

	Truncating the basis used for expansion of the coefficient function already introduces an approximation error.

	\begin{equation}\label{fpcr_reg_both_expansions}
		\begin{split}
			y_i &= \alpha + \int_{0}^{1} \left(\hat{\mu}(s) + \sum_{m \in \mathcal{M}} \hat{\xi}^{m}_i \hat{\nu}^{m}(s)\right) {\color{blue}\left(\sum_{j = 1}^{J} b_j \phi_j(s) + \delta_{\beta}^{J}(s)\right)} \mathrm{d}s + \epsilon_i\\
			&= \alpha + \sum_{j = 1}^{J} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s + \int_{0}^{1} \delta_{\beta}^{J}(s) \hat{\mu}(s) \mathrm{d}s + \sum_{m \in \mathcal{M}} \left[ \hat{\xi}^m_i \sum_{j = 1}^{J} b_j \int_{0}^{1}\hat{\nu}^m(s) \phi_j(s) \mathrm{d}s \right] \\
			& \quad \quad + \sum_{m \in \mathcal{M}} \left[ \hat{\xi}^m_i \int_{0}^{1}\hat{\nu}^m(s) \delta_{\beta}^{J}(s) \mathrm{d}s \right] + \epsilon_i
		\end{split}
	\end{equation}

	If we additionally derive and approximate the principal components and corresponding scores using a truncated basis representation as in Equation \ref{score_approx} we obtain the following. To not complicate things more than necessary, the following equation assumes that the same basis $\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ was used in the derivation of the principal components and the expansion of the coefficient function. Additionally, the following approximation also truncates the basis for the expansion of the coefficient function at the same parameter $L$ that was used for the approximation of the principal components and scores.

	For convenience, define the following notation:

	\begin{equation}
		\tilde{\alpha}^L = \alpha + \sum_{j = 1}^{L} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s + \int_{0}^{1} \delta_{\beta}^{L}(s) \hat{\mu}(s) \mathrm{d}s
	\end{equation}

	Then Equation \ref{fpcr_reg_both_expansions} can be expressed as follows.

	\begin{equation}
		\begin{split}
			y_i & = \tilde{\alpha}^L
			+ \sum_{m \in \mathcal{M}} \left[ \left(\tilde{\xi}^{m,L}_{i} + \delta_{\xi, i}^{m, L} \right) \sum_{j = 1}^{L} b_j \int_{0}^{1} \left(\tilde{\nu}^{m,L}(s) + \delta_{\nu, m}^L(s) \right) \phi_j(s) \mathrm{d}s \right] 
			+ \epsilon_i \\
			& = \tilde{\alpha}^L
			+ \sum_{m \in \mathcal{M}} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right] 
			+ \sum_{m \in \mathcal{M}} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} \delta_{\nu, m}^L(s) \phi_j(s) \mathrm{d}s \right] \\
			& \quad \quad + \sum_{m \in \mathcal{M}} \left[ \delta_{\xi, i}^{m, L} \sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right] 
			+ \sum_{m \in \mathcal{M}} \left[ \delta_{\xi, i}^{m, L} \sum_{j = 1}^{L} b_j \int_{0}^{1} \delta_{\nu, m}^L(s) \phi_j(s) \mathrm{d}s \right]
			+ \epsilon_i \\
			& \approx \tilde{\alpha}^L
			+ \sum_{m \in \mathcal{M}} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s \right] + \epsilon_i
		\end{split}
	\end{equation}

	The parameter $M$ corresponds to the chosen number of principal components and therefore constitutes another choice in the approximation.

@@

	\subsection{Motivation}
	For the simulation study, we deviate from the standard simulation setting. Instead of generating data by ourselves, we use the gasoline data which consists of 60 samples of Near-infrared (NIR) spectra measured by 2-nm from 900 to 1,700 nm, and a response variable,  the octane rating. NIR- spectroscopy allows to analyse samples of gasoline much faster, cheaper and with the same reproducibility as standard tests while not destroying the sample (cf. \cite{Bohacs_Ovadi_Salgo1998}). We chose this setup to improve the approach towards the application in which we  predict the octane ratings from the gasoline dataset.

@@

	\section{Proofs}
	\subsection{Lemma} \label{Proof1}
	The curves $X(t) \in \mathbb{L}^2[0,1]$ is expanded by the eigenfunctions $\{\nu_j\}$ as (\ref{KarhunenLoeve}). The coefficients $\xi_{j}$ of basis functions satisfy the following properties:
	\begin{enumerate}
		\item $\mathbb{E}[\xi_{j}] = 0$
		\item $\mathbb{E}[\xi_{j} \xi_{k}] = \lambda_{j}$, if $j = k$, otherwise 0
		\item Var[$\xi_{j}$] = $\lambda_{j}$
	\end{enumerate}

	\begin{proof}
		Assume that $F(t)$ is the centered process of $X(t)$, namely, $F(t) = X(t) - \int_{\Omega}X(t)dP(\omega)$. To obtain the first result, we can show that
		\begin{equation}\label{Lemma1}
			\begin{split}
				\mathbb{E}[\xi_{j}] = & \mathbb{E} \biggl\lbrack \int_{0}^{1} F(t) \nu_{j}(t)dt\biggr\rbrack\\
				= & \int_{\Omega} \int_{0}^{1} F(t) \nu_{j}(t) dt dP(\omega)\\
				= & \int_{0}^{1} \int_{\Omega} F(t) \nu_{j}(t) dP(\omega) dt \quad \text{(Fubini)}\\
				= & \int_{0}^{1} {\color{red}\int_{\Omega} F(t) dP(\omega)} \nu_{j}(t) dt\\
				= & \int_{0}^{1} {\color{red}\mathbb{E}[F(t)]} \nu_{j}(t) dt = 0
			\end{split}
		\end{equation}
		where $\mathbb{E}[F(t)]$ is 0 since $F(t)$ is a centered process.
		The second claim is proved as:
		\begin{equation}\label{Lemma2}
			\begin{split}
				\mathbb{E} [\xi_{j} \xi_{k}] = & \mathbb{E}  \biggl\lbrack \int_{0}^{1} F(s) \nu_{j}(s)ds \int_{0}^{1} F(t) \nu_{k}(t)dt  \biggr\rbrack\\
				= & \mathbb{E} \biggl\lbrack {\int_{0}^{1} \int_{0}^{1} F(s) \nu_{j}(s) F(t) \nu_{k}(t) ds dt} \biggr\rbrack \quad \text{(Fubini)}\\
				= & \int_{0}^{1} \int_{0}^{1} {\color{red}\mathbb{E}[{F(s)F(t)}]} \nu_{j}(s) \nu_{k}(t) ds dt\\
				= & \int_{0}^{1} {\color{red}\left(\int_{0}^{1}c(s,t)\nu_{j}(s)ds \right)} \nu_{k}(t) dt \\
				= & \int_{0}^{1}{\color{red}[K\nu_{j}](t)}\nu_{k}(t)dt\\
				= & \langle K \nu_{j}, \nu_{k} \rangle\\
				= & \langle \lambda_{j} \nu_{j}, \nu_{k} \rangle = \lambda_{j} \quad \text{if $j = k$, otherwise 0}
			\end{split}
		\end{equation}
		where the result is produced from orthonormaility of the eigenfunctions. The last assertion is confirmed from the above two properties.
		\begin{equation}\label{Lemma3}
			Var[\xi_{i}] = \mathbb{E}\left[(\xi_{i} - \mathbb{E}[\xi_{i}])^{2}\right] = \mathbb{E}[\xi_{i}^{2}] = \lambda_{i}
		\end{equation}
		The original process also has the same properties as the centered one since
		\begin{equation}
			X(t) = F(t) + \mathbb{E}[X(t)] = \mu(t) + \sum_{j=1}^{\infty}\xi_{j}\nu_{j}(t)
		\end{equation}
	\end{proof}

>>>>

	\subsection{Inner Products and Hilbert Spaces}
	Let $\mathbb{V}$ be a vector space over some field of scalars $\mathbb{F}$. {\color{orange} How about hereby restricting the $\mathbb{F} = \mathbb{R}$, otherwise we would need to put something additional at 4.}A function $\langle \cdot, \cdot \rangle : \mathbb{V} \times  \mathbb{V} \rightarrow \mathbb{F}$ is called an inner product, if $\forall v, v_1, v_2 \in \mathbb{V}$ and $a_1, a_2 \in \mathbb{F}$ the following properties hold.

@@

	A vector space with an associated inner product is called an inner product space. {\color{red}[verbatim quote!]}
	The inner product naturally defines a norm and an associated distance on the vector space as follows. In the following we restrict our analysis to the case of $\mathbb{F} = \mathbb{R}$.

@@

	\subsection{Hilbert Space of Square-Integrable Functions}
	In functional data analysis, one Hilbert space of particular importance is the space of square-integrable functions on $[0,1]$ denoted $\mathbb{L}^2[0,1]$. To define it, look first at the measure space given by $([0,1], \mathcal{B}, \mu)$ where $\mathcal{B}$ is the Borel $\sigma$-algebra on $[0,1]$ and $\mu$ is the Lebesgue-measure. Then $\mathbb{L}^2[0,1]$ is the collection of all measurable functions $f$ on $[0,1]$ that fulfill the following condition.

@@

	$\mathbb{L}^2[0,1]$ is the function space that is most often used for theoretical considerations in functional data analysis without loss of generality. We also focus on the interval [0,1] for the purpose of this paper.	The random function defined on $\mathbb{L}^2[0,1]$ can be represented as

	%Trivially, it is possible to extend this to other closed intervals on the reals line, but there are also more complex generalizations. For the purpose of this paper we will focus on the typical case and assume that random functions are random variables realizing in $\mathbb{L}^2$ for some closed interval of the real numbers.

	\begin{equation}
	\{f(t,\omega) : t \in [0, 1], \omega \in \Omega\}
	\end{equation}

	The realized $f(t)$ for every $t \in [0,1]$ is called a sample curve for the process. The collection of such sample curves constitutes a functional data set.

	\subsection{Bases of $\mathbb{L}^2$} 
	{\color{red} Maybe change title due to monomial and bspline basis not fulfilling this property.}
	As previously described, a basis of a Hilbert space can be used to express elements of the space using the corresponding Fourier expansion. Two examples of bases that are often used in practice to express / approximate elements of $\mathbb{L}^2[0,1]$  are explained in the following.

@@

	\paragraph{Monomial Basis}
	{\color{red} No shift parameter in implementation in fda.}
This is the basis that is needed to build polynomials, one of the best-known ways to expand a function.
The polynomial of the form

@@

	In reality these calculations are often done using basis representations of both the functional principal components $\hat{\nu}^m$ and the observations $x_i(t)$ leading to the following representation.

	\begin{equation}\label{FPCA_basis_expansion}
		\begin{split}
			\hat{\xi}_{i}^m & = \int_{0}^{1} {\color{red}\left( x_i(s) - \hat{\mu}(s)\right)} {\color{blue}\hat{\nu}^m(s)} \mathrm{d}s
			= \int_{0}^{1} {\color{red}\left(\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)\right)} {\color{blue}\left(\sum_{k \in \mathcal{L}} b_{k}^m \psi_{k}(s)\right)} \mathrm{d}s \\
			& = \sum_{j \in \mathcal{I}} \left[ a_{i,j}\sum_{k \in \mathcal{L}} b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s\right] \approx \sum_{j = 1}^{J} \left[a_{i,j}\sum_{k = 1}^{K} b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right]
		\end{split}
	\end{equation}

@@

	\begin{equation}\label{score_approx}
		\hat{\xi}_{i}^m \approx \sum_{j = 1}^{L} \left[ a_{i,j}\sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \phi_j(s) \phi_{k}(s)\mathrm{d}s\right] =: \tilde{\xi}^{m,L}_{i}
	\end{equation}

@@

	\subsubsection{Estimation using Basis-Representation}
	The most common way to make this problem tractable is via a basis representation of $\beta(t)$. Therefore, let $\{b_i(t) \: \vert \: i \in \mathbb{N}\}$ be a basis of $\mathbb{L}^2[0,1]$ and represent $\beta(t)$ in terms of this basis.

	\begin{equation}
		\beta(t) = \sum_{j = 1}^{\infty} b_j \phi_j(t)
	\end{equation}

@@

	\begin{equation}
			Y(\omega) \approx \alpha + \sum_{j = 1}^{L} b_j Z_j(\omega) + \epsilon(\omega)
	\end{equation}

@@

	\begin{equation}\label{basis_exp_transf}
		\begin{split}
			Y(\omega) & = \alpha + \int_{0}^{1} {\color{blue}\beta(s)} {\color{red}X(\omega)(s)}\mathrm{d}s + \epsilon(\omega)
			 = \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} b_j  \phi_j(s)\right)} {\color{red}\left(\sum_{k \in \mathcal{L}} d_k(\omega)  \psi_k(s)\right)} \right]\mathrm{d}s + \epsilon(\omega) \\
			& = \alpha + \sum_{j \in \mathcal{I}} b_j \left[\sum_{k \in \mathcal{L}} d_k(\omega) \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s\right] + \epsilon(\omega) 
			\approx \alpha + \sum_{j = 1}^{J} \left[b_j \sum_{k = 1}^{K}  d_k(\omega) \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s\right] + \epsilon(\omega)
		\end{split}
	\end{equation}

@@

	\begin{equation}
			\tilde{Z}_j(\omega) = \sum_{k = 1}^{L} \left[d_k(\omega) \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \right] \quad j = 1, \dots, L
	\end{equation}

@@

	\begin{equation}\label{simplified_model_basis_equation}
		Y(\omega) \approx \alpha + \sum_{j = 1}^{J} b_j \tilde{Z}_j(\omega) + \epsilon(\omega)
	\end{equation}

@@

	\begin{equation}
		\begin{split}
			Y(\omega) &= \alpha + \int_{0}^{1} {\color{red}X(\omega)(s)} \beta(s) \mathrm{d}s + \epsilon(\omega)
			= \alpha + \int_{0}^{1} {\color{red}\left(\mu(s) + \sum_{m \in \mathbb{N}} \xi^m(\omega) \nu^m(s)\right)} \beta(s) \mathrm{d}s + \epsilon(\omega)\\
			&= {\color{teal}\alpha + \int_{0}^{1} \mu(s) \beta(s) \mathrm{d}s} + \sum_{m \in \mathbb{N}} \xi^m(\omega) {\color{violet}\int_{0}^{1} \nu^m(s) \beta(s) \mathrm{d}s} + \epsilon(\omega)
			= {\color{teal}\bar{\alpha}} + \sum_{m \in \mathbb{N}} \xi^m(\omega) {\color{violet}\beta^m} + \epsilon(\omega)
		\end{split}
	\end{equation}

@@

	If we additionally derive and approximate the principal components and corresponding scores using a truncated basis representation as in Equation \ref{score_approx} we obtain the following. To not complicate things more than necessary, the following equation assumes that the same basis $\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ was used in the derivation of the principal components and the expansion of the coefficient function. Additionally, the following approximation also truncates the basis for the expansion of the coefficient function at the same parameter $L$ that was used for the approximation of the principal components and scores. The parameter $M$ corresponds to the chosen number of principal components and therefore constitutes another choice in the approximation.

	\begin{equation}
		\begin{split}
			y_i & \approx {\color{teal}\alpha + \sum_{j = 1}^{L} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s} +  \sum_{m  = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} {\color{blue}\hat{\nu}^{m,L}(s)} \phi_j(s) \mathrm{d}s \right] + \epsilon_i \\
			& \approx {\color{teal} \tilde{\alpha}} + \sum_{m  = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1}{\color{blue}\left(\sum_{k = 1}^{L} n_{k}^m \phi_{k}(s)\right)} \phi_j(s) \mathrm{d}s \right] + \epsilon_i \\
			& \approx \tilde{\alpha} + \sum_{m  = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} {\color{red}\sum_{j = 1}^{L} \left[ b_j \sum_{k = 1}^{L} n_{k}^m \int_{0}^{1} \phi_{k}(s) \phi_j(s) \mathrm{d}s \right]} \right]+ \epsilon_i
			= \tilde{\alpha} + \sum_{m  = 1}^{M} \tilde{\xi}^{m,L}_{i} {\color{red}\tilde{\beta}^{m,L}}+ \epsilon_i
		\end{split}
	\end{equation}

@@

	\subsection{Motivation}

	In the simulation study, we deviate from the standard simulation setting. Instead of generating data by ourselves, we use the gasoline data which consists of 60 samples of Near-infrared (NIR) spectra measured by 2-nm from 900 to 1,700 nm, and a response variable,  the octane rating. We chose this setup to improve the approach towards the application in which we  predict the octane ratings from the gasoline dataset.

	 To exploit the regularity of the curves of the spectra, we introduced different basis functions and demonstrated the importance of the truncation parameter $\mathcal{K}$ for the estimation in SECTION HERE. For the simulation study, we rely on the introduced estimation strategies with the introduced basis functions and focus on choosing the truncation parameter $\mathcal{K}$ as well as the number of FPC, which is as well affected by $\mathcal{K}$, by ten fold cross-validation. While cross-validation is common for selecting $\mathcal{K}$, the number of FPC in practice is often truncated after a prespecified amount of explained variability \cite{kokoszka_introduction_2017}, which might not be optimal since FPC with smaller eigenvalues may have greater influence on the prediction \cite{Jolliffe_1982}.

	 This setup is opposing to the often used penalized functional regression as described by \citep{Goldsmith_2011} in which an explicit smoothness constraint $\lambda$ is used to tune the smoothness of the estimator $\hat{\beta}(t)$ while setting the $K$ sufficiently high. This would avoid the heavy computing of validating the best value for $K$ which we will conduct in the simulation. To provide intuition in this approach, let 
	 \begin{equation}
	 	PSSE_\lambda(\alpha, \beta) = \sum_{i = 1}^{N} (Y_i -\alpha -\int_0^1 \beta(t)X_i(t)dt)^2 + \lambda * \int (D^m\beta(t))^2 dt
	 \end{equation}
	 denote the penalized residual sum of squares as notated by \cite{ramsay_functional_2005} for the derivative of order $m$. A typical choice is the second derivative as highly variable functions are expected to yield large second derivatives and therefore a larger penalty. The smoothing parameter $\lambda$ is set to minimize the $PSSE_\lambda(\alpha, \beta)$, which can be archived by different criteria as shown in \cite{ThomasLee_2003}

	%While this paper and its simulation does not touch upon the topic of roughness penalties in estimation and their selection, other simulations focus e.g. on choosing the knots of penalized splines (David Ruppert 2000) or the important choice of the smoothing parameter selection method (Thomas C.M. Lee, 2002). An overview about other variable selections methods for functional regression with an origin in the multivariate regression setting can be found in( G. Aneiros, S. Novo and P. Vieu)

	%In the simulation study, we deviate from the standard simulation setting. Instead of generating data by ourselves, we use the gasoline data which consists of 60 samples of Near-infrared (NIR) spectra measured by 2-nm from 900 to 1,700 nm, and a response variable,  the octane rating. We chose this setup to improve the approach towards the application in which we  predict the octane ratings from the gasoline dataset.

@@

	\section{Proofs}
	\subsection{Lemma} \label{Proof1}
	{\color{orange} We might put the below theorems for KL. The deterministic basis expansions are pretty clear about why we can use the truncation version by itself. In contrast, I feel like that for the case of KL it does not. And in the centered case?} 
	The coefficients $\xi_{j}$ satisfy the following:
	\begin{enumerate}
		\item $\mathbb{E}[\xi_{j}] = 0$
		\item $\mathbb{E}[\xi_{j} \xi_{k}] = \lambda_{j}$, if $j = k$, otherwise 0
		\item Var[$\xi_{j}$] = $\lambda_{j}$
	\end{enumerate}

	\begin{proof}
		To obtain the first result, we can show that
		\begin{equation}
			\begin{split}
				\mathbb{E}[\xi_{j}] = & \mathbb{E} \biggl\lbrack \int_{0}^{1} F(t) \nu_{j}(t)dt \biggr\rbrack\\
				= & \int_{\Omega} \int_{0}^{1} F(t) \nu_{j}(t) dt dP(\omega)\\
				= & \int_{0}^{1} \int_{\Omega} F(t) \nu_{j}(t) dP(\omega) dt \quad \text{(Fubini)}\\
				= & \int_{0}^{1} \mathbb{E}[F(t)] \nu_{j}(t) dt\\
				= & \mu(t) \int_{0}^{1} \nu_{j}(t)\\
				= & \mu(t) \langle \nu_{j}(t), 1 \rangle = 0
			\end{split}
		\end{equation}
		where the constant function is always an eigenfunction of the operater $K$. It leads the inner product to 0 due to orthonormality of eigenfunctions. {\color{red} Another way to prove or use centered mean}
		For the case of centered process
		\begin{equation}\label{Lemma1}
			\begin{split}
				\mathbb{E}[\xi_{j}] = & \mathbb{E} \biggl\lbrack \int_{0}^{1} F(t) \nu_{j}(t)dt\biggr\rbrack\\
				= & \int_{\Omega} \int_{0}^{1} F(t) \nu_{j}(t) dt dP(\omega)\\
				= & \int_{0}^{1} \int_{\Omega} F(t) \nu_{j}(t) dP(\omega) dt \quad \text{(Fubini)}\\
				= & \int_{0}^{1} \mathbb{E}[F(t)] \nu_{j}(t) dt = 0
			\end{split}
		\end{equation}
		where $\mathbb{E}[F(t)]$ is 0 since $F(t)$ is a centered process.
		The second claim is proved as:
		\begin{equation}\label{Lemma2}
			\begin{split}
				\mathbb{E} [\xi_{j} \xi_{k}] = & \mathbb{E}  \biggl\lbrack \int_{0}^{1} F(s) \nu_{j}(s)ds \int_{0}^{1} F(t) \nu_{k}(t)dt  \biggr\rbrack\\
				= & \mathbb{E} \biggl\lbrack {\int_{0}^{1} \int_{0}^{1} F(s) \nu_{j}(s) F(t) \nu_{k}(t) ds dt} \biggr\rbrack \quad \text{(Fubini)}\\
				= & \int_{0}^{1} \int_{0}^{1} \mathbb{E}[{F(s)F(t)}] \nu_{j}(s) \nu_{k}(t) ds dt\\
				= & \int_{0}^{1} \left(\int_{0}^{1}c(s,t)\nu_{j}(s)ds \right) \nu_{k}(t) dt \\
				= & \int_{0}^{1}[K\nu_{j}](t)\nu_{k}(t)dt\\
				= & \langle K \nu_{j}, \nu_{k} \rangle\\
				= & \langle \lambda_{j} \nu_{j}, \nu_{k} \rangle = \lambda_{j} \quad \text{if $j = k$, otherwise 0}
			\end{split}
		\end{equation}
		where the result is produced from orthonormaility of the eigenfunctions. The last assertion is confirmed from the other two properties.
		\begin{equation}\label{Lemma3}
			Var[\xi_{i}] = \mathbb{E}\left[(\xi_{i} - \mathbb{E}[\xi_{i}])^{2}\right] = \mathbb{E}[\xi_{i}^{2}] = \lambda_{i}
		\end{equation}
	\end{proof}
